/* CHAPTER 1. Basics */

/*
 * cpdf_fromFile(filename, userpw) loads a PDF file from a given file. Supply
 * a user password (possibly blank) in case the file is encrypted. It won't be
 * decrypted, but sometimes the password is needed just to load the file.
 */
int cpdf_fromFile(const char[], const char[]);

/*
 * cpdf_fromFileLazy(pdf, userpw) loads a PDF from a file, doing only minimal
 * parsing. The objects will be read and parsed when they are actually
 * needed. Use this when the whole file won't be required. Also supply a user
 * password (possibly blank) in case the file is encrypted. It won't be
 * decrypted, but sometimes the password is needed just to load the file.
 */
int cpdf_fromFileLazy(const char[], const char[]);

/*
 * cpdf_fromMemory(data, length, userpw) loads a file from memory, given a
 * pointer and a length, and the user password.
 */
int cpdf_fromMemory(void *, int, const char[]);

/*
 * cpdf_fromMemory(data, length, userpw) loads a file from memory, given a
 * pointer and a length, and the user password, but lazily like
 * cpdf_fromFileLazy.
 */
int cpdf_fromMemoryLazy(void *, int, const char[]);

/*
 * cpdf_blankDocument(width, height, num_pages) creates a blank document with
 * pages of the given width (in points), height (in points), and number of
 * pages.
 */
int cpdf_blankDocument(double, double, int);

/* Standard page sizes. */
enum cpdf_papersize {
  cpdf_a0portrait,        /* A0 portrait */
  cpdf_a1portrait,        /* A1 portrait */
  cpdf_a2portrait,        /* A2 portrait */
  cpdf_a3portrait,        /* A3 portrait */
  cpdf_a4portrait,        /* A4 portrait */
  cpdf_a5portrait,        /* A5 portrait */
  cpdf_a0landscape,       /* A0 landscape */
  cpdf_a1landscape,       /* A1 landscape */
  cpdf_a2landscape,       /* A2 landscape */
  cpdf_a3landscape,       /* A3 landscape */
  cpdf_a4landscape,       /* A4 landscape */
  cpdf_a5landscape,       /* A5 landscape */
  cpdf_usletterportrait,  /* US Letter portrait */
  cpdf_usletterlandscape, /* US Letter landscape */
  cpdf_uslegalportrait,   /* US Legal portrait */
  cpdf_uslegallandscape   /* US Legal landscape */
};

/*
 * cpdf_blankDocumentPaper(papersize, num_pages) makes a blank document given
 * a page size and number of pages.
 */
int cpdf_blankDocumentPaper(enum cpdf_papersize, int);

/* Remove a PDF from memory, given its number. */
void cpdf_deletePdf(int);

/*
 * Calling cpdf_replacePdf(a, b) places PDF b under number a. Number b is no
 * longer available.
 */
void cpdf_replacePdf(int, int);

/*
 * To enumerate the list of currently allocated PDFs, call
 * cpdf_startEnumeratePDFs which gives the number, n, of PDFs allocated, then
 * cpdf_enumeratePDFsInfo and cpdf_enumeratePDFsKey with index numbers from
 * 0...(n - 1). Call cpdf_endEnumeratePDFs to clean up.
 */
int cpdf_startEnumeratePDFs(void);
int cpdf_enumeratePDFsKey(int);
char *cpdf_enumeratePDFsInfo(int);
void cpdf_endEnumeratePDFs(void);

/* Convert a figure in centimetres to points (72 points to 1 inch) */
double cpdf_ptOfCm(double);

/* Convert a figure in millimetres to points (72 points to 1 inch) */
double cpdf_ptOfMm(double);

/* Convert a figure in inches to points (72 points to 1 inch) */
double cpdf_ptOfIn(double);

/* Convert a figure in points to centimetres (72 points to 1 inch) */
double cpdf_cmOfPt(double);

/* Convert a figure in points to millimetres (72 points to 1 inch) */
double cpdf_mmOfPt(double);

/* Convert a figure in points to inches (72 points to 1 inch) */
double cpdf_inOfPt(double);

/*
 * A page range is a list of page numbers used to restrict operations to
 * certain pages. A page specification is a textual description of a page
 * range, such as "1-12,18-end". Here is the syntax:
 *
 * o A range must contain no spaces.
 *
 * o A dash (-) defines ranges, e.g. 1-5 or 6-3.
 *
 * o A comma (,) allows one to specify several ranges, e.g. 1-2,4-5.
 *
 * o The word end represents the last page number.
 *
 * o The words odd and even can be used in place of or at the end of a page
 * range to restrict to just the odd or even pages.
 *
 * o The words portrait and landscape can be used in place of or at the end of
 * a page range to restrict to just those pages which are portrait or
 * landscape. Note that the meaning of "portrait" and "landscape" does not
 * take account of any viewing rotation in place (use cpdf_upright first, if
 * required). A page with equal width and height is considered neither
 * portrait nor landscape.
 *
 * o The word reverse is the same as end-1.
 *
 * o The word all is the same as 1-end.
 *
 * o A tilde (~) defines a page number counting from the end of the document
 * rather than the beginning. Page ~1 is the last page, ~2 the penultimate
 * page etc.
 */

/*
 * cpdf_parsePagespec(pdf, range) parses a page specification with reference
 * to a given PDF (the PDF is supplied so that page ranges which reference
 * pages which do not exist are rejected).
 */
int cpdf_parsePagespec(int, const char[]);

/*
 * cpdf_validatePagespec(range) validates a page specification so far as is
 * possible in the absence of the actual document. Result is true if valid.
 */
int cpdf_validatePagespec(const char[]);

/*
 * cpdf_stringOfPagespec(pdf, range) builds a page specification from a page
 * range. For example, the range containing 1,2,3,6,7,8 in a document of 8
 * pages might yield "1-3,6-end"
 */
char *cpdf_stringOfPagespec(int, int);

/* cpdf_blankRange() creates a range with no pages in. */
int cpdf_blankRange(void);

/* cpdf_deleteRange(range) deletes a range. */
void cpdf_deleteRange(int);

/*
 * cpdf_range(from, to) builds a range from one page to another inclusive. For
 * example, cpdf_range(3,7) gives the range 3,4,5,6,7
 */
int cpdf_range(int, int);

/* cpdf_all(pdf) is the range containing all the pages in a given document. */
int cpdf_all(int);

/*
 * cpdf_even(range) makes a range which contains just the even pages of
 * another range.
 */
int cpdf_even(int);

/*
 * cpdf_odd(range) makes a range which contains just the odd pages of another
 * range.
 */
int cpdf_odd(int);

/*
 * cpdf_rangeUnion(a, b) makes the union of two ranges giving a range
 * containing the pages in range a and range b.
 */
int cpdf_rangeUnion(int, int);

/*
 * cpdf_difference(a, b) makes the difference of two ranges, giving a range
 * containing all the pages in a except for those which are also in b.
 */
int cpdf_difference(int, int);

/* cpdf_removeDuplicates(range) deduplicates a range, making a new one. */
int cpdf_removeDuplicates(int);

/* cpdf_rangeLength gives the number of pages in a range. */
int cpdf_rangeLength(int);

/*
 * cpdf_rangeGet(range, n) gets the page number at position n in a range,
 * where n runs from 0 to rangeLength - 1.
 */
int cpdf_rangeGet(int, int);

/*
 * cpdf_rangeAdd(range, page) adds the page to a range, if it is not already
 * there.
 */
int cpdf_rangeAdd(int, int);

/*
 * cpdf_isInRange(range, page) returns true if the page is in the range,
 * false otherwise.
 */
int cpdf_isInRange(int, int);

/* cpdf_pages(pdf) returns the number of pages in a PDF. */
int cpdf_pages(int);

/*
 * cpdf_pagesFast(password, filename) returns the number of pages in a given
 * PDF, with given user encryption password. It tries to do this as fast as
 * possible, without loading the whole file.
 */
int cpdf_pagesFast(const char[], const char[]);

/*
 * cpdf_toFile (pdf, filename, linearize, make_id) writes the file to a given
 * filename. If linearize is true, it will be linearized if a linearizer is
 * available. If make_id is true, it will be given a new ID.
 */
void cpdf_toFile(int, const char[], int, int);

/*
 * cpdf_toFile (pdf, filename, linearize, make_id, preserve_objstm,
 * generate_objstm, compress_objstm) writes the file to a given filename. If
 * make_id is true, it will be given a new ID.  If preserve_objstm is true,
 * existing object streams will be preserved. If generate_objstm is true,
 * object streams will be generated even if not originally present. If
 * compress_objstm is true, object streams will be compressed (what we
 * usually want). WARNING: the pdf argument will be invalid after this call,
 * and should be discarded.
 */
void cpdf_toFileExt(int, const char[], int, int, int, int, int);

/*
 * Given a buffer of the correct size, cpdf_toFileMemory (pdf, linearize,
 * make_id, &length) writes it and returns the buffer. The buffer length is
 * filled in &length.
 */
void *cpdf_toMemory(int, int, int, int *);

/*
 * cpdf_isEncrypted(pdf) returns true if a documented is encrypted, false
 * otherwise.
 */
int cpdf_isEncrypted(int);

/*
 * cpdf_decryptPdf(pdf, userpw) attempts to decrypt a PDF using the given
 * user password. The error code is non-zero if the decryption fails.
 */
void cpdf_decryptPdf(int, const char[]);

/*
 * cpdf_decryptPdfOwner(pdf, ownerpw) attempts to decrypt a PDF using the
 * given owner password. The error code is non-zero if the decryption fails.
 */
void cpdf_decryptPdfOwner(int, const char[]);

/*
 * File permissions. These are inverted, in the sense that the presence of
 * one of them indicates a restriction.
 */
enum cpdf_permission {
  cpdf_noEdit,     /* Cannot edit the document */
  cpdf_noPrint,    /* Cannot print the document */
  cpdf_noCopy,     /* Cannot copy the document */
  cpdf_noAnnot,    /* Cannot annotate the document */
  cpdf_noForms,    /* Cannot edit forms in the document */
  cpdf_noExtract,  /* Cannot extract information */
  cpdf_noAssemble, /* Cannot assemble into a bigger document */
  cpdf_noHqPrint   /* Cannot print high quality */
};

/*
 * Encryption methods. Suffixes 'false' and 'true' indicates lack of or
 * presence of encryption for XMP metadata streams.
 */
enum cpdf_encryptionMethod {
  cpdf_pdf40bit,          /* 40 bit RC4 encryption */
  cpdf_pdf128bit,         /* 128 bit RC4 encryption */
  cpdf_aes128bitfalse,    /* 128 bit AES encryption, do not encrypt
                           * metadata. */
  cpdf_aes128bittrue,     /* 128 bit AES encryption, encrypt metadata */
  cpdf_aes256bitfalse,    /* Deprecated. Do not use for new files */
  cpdf_aes256bittrue,     /* Deprecated. Do not use for new files */
  cpdf_aes256bitisofalse, /* 256 bit AES encryption, do not encrypt
                           * metadata. */
  cpdf_aes256bitisotrue   /* 256 bit AES encryption, encrypt metadata */
};

/*
 * cpdf_toFileEncrypted(pdf, encryption_method, permissions,
 * permission_length, owner_password, user password, linearize, makeid,
 * filename) writes a file as encrypted.
 */
void cpdf_toFileEncrypted(int, int, int *, int, const char[], const char[], int,
                          int, const char[]);

/*
 * cpdf_toFileEncryptedExt(pdf, encryption_method, permissions,
 * permission_length, owner_password, user_password, linearize, makeid,
 * preserve_objstm, generate_objstm, compress_objstm, filename) WARNING: the
 * pdf argument will be invalid after this call, and should be discarded.
 */
void cpdf_toFileEncryptedExt(int, int, int *, int, const char[], const char[],
                             int, int, int, int, int, const char[]);

/*
 * cpdf_hasPermission(pdf, permission) returns true if the given permission
 * (restriction) is present.
 */
int cpdf_hasPermission(int, enum cpdf_permission);

/*
 * cpdf_encryptionKind(pdf) return the encryption method currently in use on
 * a document.
 */
enum cpdf_encryptionMethod cpdf_encryptionKind(int);

