/* CHAPTER 3. Pages */

/*
 * cpdf_scalePages(pdf, range, x scale, y scale) scales the page dimensions
 * and content by the given scale, about (0, 0). Other boxes (crop etc. are
 * altered as appropriate)
 */
void cpdf_scalePages(int, int, double, double);

/*
 * cpdf_scaleToFit(pdf, range, width height, scale) scales the content to fit
 * new page dimensions (width x height) multiplied by scale (typically 1.0).
 * Other boxed (crop etc. are altered as appropriate)
 */
void cpdf_scaleToFit(int, int, double, double, double);

/*
 * cpdf_scaleToFitPaper(pdf, range, papersize, scale) scales the page content
 * to fit the given page size, possibly multiplied by scale (typically 1.0)
 */
void cpdf_scaleToFitPaper(int, int, enum cpdf_papersize, double);

/* Positions on the page. Used for scaling about a point, and adding text. */
enum cpdf_anchor {
  cpdf_posCentre,      /* Absolute centre */
  cpdf_posLeft,        /* Absolute left */
  cpdf_posRight,       /* Absolute right */
  cpdf_top,            /* Top top centre of the page */
  cpdf_topLeft,        /* The top left of the page */
  cpdf_topRight,       /* The top right of the page */
  cpdf_left,           /* The left hand side of the page, halfway
                        * down */
  cpdf_bottomLeft,     /* The bottom left of the page */
  cpdf_bottom,         /* The bottom middle of the page */
  cpdf_bottomRight,    /* The bottom right of the page */
  cpdf_right,          /* The right hand side of the page, halfway
                        * down */
  cpdf_diagonal,       /* Diagonal, bottom left to top right */
  cpdf_reverseDiagonal /* Diagonal, top left to bottom right */
};

/*
 * A cpdf_position is an anchor (above) and zero or one or two parameters
 * (cpdf_coord1, cpdf_coord2).
 *
 * cpdf_posCentre: Two parameters, x and y
 *
 * cpdf_posLeft: Two parameters, x and y
 *
 * cpdf_posRight: Two parameters, x and y
 *
 * cpdf_top: One parameter -- distance from top
 *
 * cpdf_topLeft: One parameter -- distance from top left
 *
 * cpdf_topRight: One parameter -- distance from top right
 *
 * cpdf_left: One parameter -- distance from left middle
 *
 * cpdf_bottomLeft: One parameter -- distance from bottom left
 *
 * cpdf_bottom: One parameter -- distance from bottom
 *
 * cpdf_bottomRight: One parameter -- distance from bottom right
 *
 * cpdf_right: One parameter -- distance from right
 *
 * cpdf_diagonal: Zero parameters
 *
 * cpdf_reverseDiagonal: Zero parameters
 */
struct cpdf_position {
  int cpdf_anchor;    /* Position anchor */
  double cpdf_coord1; /* Parameter one */
  double cpdf_coord2; /* Parameter two */
};

/*
 * cpdf_scaleContents(pdf, range, position, scale) scales the contents of the
 * pages in the range about the point given by the cpdf_position, by the
 * scale given.
 */
void cpdf_scaleContents(int, int, struct cpdf_position, double);

/*
 * cpdf_shiftContents(pdf, range, dx, dy) shifts the content of the pages in
 * the range.
 */
void cpdf_shiftContents(int, int, double, double);

/*
 * cpdf_rotate(pdf, range, rotation) changes the viewing rotation to an
 * absolute value. Appropriate rotations are 0, 90, 180, 270.
 */
void cpdf_rotate(int, int, int);

/*
 * cpdf_rotateBy(pdf, range, rotation) changes the viewing rotation by a
 * given number of degrees. Appropriate values are 90, 180, 270.
 */
void cpdf_rotateBy(int, int, int);

/*
 * cpdf_rotateContents(pdf, range, angle) rotates the content about the
 * centre of the page by the given number of degrees, in a clockwise
 * direction.
 */
void cpdf_rotateContents(int, int, double);

/*
 * cpdf_upright(pdf, range) changes the viewing rotation of the pages in the
 * range, counter-rotating the dimensions and content such that there is no
 * visual change.
 */
void cpdf_upright(int, int);

/* cpdf_hFlip(pdf, range) flips horizontally the pages in the range. */
void cpdf_hFlip(int, int);

/* cpdf_vFlip(pdf, range) flips vertically the pages in the range. */
void cpdf_vFlip(int, int);

/*
 * cpdf_crop(pdf, range, x, y, w, h) crops a page, replacing any existing
 * crop box. The dimensions are in points.
 */
void cpdf_crop(int, int, double, double, double, double);

/* cpdf_removeCrop(pdf, range) removes any crop box from pages in the range. */
void cpdf_removeCrop(int, int);

/* cpdf_removeTrim(pdf, range) removes any crop box from pages in the range. */
void cpdf_removeTrim(int, int);

/* cpdf_removeArt(pdf, range) removes any crop box from pages in the range. */
void cpdf_removeArt(int, int);

/* cpdf_removeBleed(pdf, range) removes any crop box from pages in the range. */
void cpdf_removeBleed(int, int);

/*
 * cpdf_trimMarks(pdf, range) adds trim marks to the given pages, if the
 * trimbox exists.
 */
void cpdf_trimMarks(int, int);

/* cpdf_showBoxes(pdf, range) shows the boxes on the given pages, for debug. */
void cpdf_showBoxes(int, int);

/* cpdf_hardBox make a given box a 'hard box' i.e clips it explicitly. */
void cpdf_hardBox(int, int, const char[]);

