// Enumerations

/** Permission: cannot edit the document */
public static int noEdit = 0;
/** Permission: cannot print the document */
public static int noPrint = 1;
/** Permission: cannot copy the document */
public static int noCopy = 2;
/** Permission: cannot annotate the document */
public static int noAnnot = 3;
/** Permission: cannot edit forms in the document */
public static int noForms = 4;
/** Permission: cannot extract information */
public static int noExtract = 5;
/** Permission: cannot assemble into a bigger document */
public static int noAssemble = 6;
/** Permission: cannot print high quality */
public static int noHqPrint = 7;

/** Encryption method: 40 bit RC4 encryption */
public static int pdf40bit = 0;
/** Encryption method: 128 bit RC4 encryption */
public static int pdf128bit = 1;
/** Encryption method: 128 bit AES encryption, do not encrypt metadata */
public static int aes128bitfalse = 2;
/** Encryption method: 128 bit AES encryption, encrypt metadata */
public static int aes128bittrue = 3;
/** Encryption method: Deprecated. Do not use for new files */
public static int aes256bitfalse = 4;
/** Encryption method: Deprecated. Do not use for new files */
public static int aes256bittrue = 5;
/** Encryption method: 256 bit AES encryption, do not encrypt metadata */
public static int aes256bitisofalse = 6;
/** Encryption method: 256 bit AES encryption, encrypt metadata */
public static int aes256bitisotrue = 7;

/** Page label style: 1, 2, 3... */
public static int decimalArabic = 0;
/** Page label style: I, II, III... */
public static int uppercaseRoman = 1;
/** Page label style: i, ii, iii... */
public static int lowercaseRoman = 2;
/** Page label style: A, B, C... */
public static int uppercaseLetters = 3;
/** Page label style: a, b, c...*/
public static int lowercaseLetters = 4;

/** Layout: single page */
public static int singlePage = 0;
/** Layout: one column */
public static int oneColumn = 1;
/** Layout: two column left */
public static int twoColumnLeft = 2;
/** Layout: two column right */
public static int twoColumnRight = 3;
/** Layout: two page left */
public static int twoPageLeft = 4;
/** Layout: two page right */
public static int twoPageRight = 5;

/** Page mode: use none */
public static int useNone = 0;
/** Page mode: use outlines */
public static int useOutlines = 1;
/** Page mode: use thumbs */
public static int useThumbs = 2;
/** Page mode: use OC */
public static int useOC = 3;
/** Page mode: use Attachments */
public static int useAttachments = 4;

/** Paper size: A0 Portrait */
public static int a0portrait = 0;
/** Paper size: A1 Portrait */
public static int a1portrait = 1;
/** Paper size: A2 Portrait */
public static int a2portrait = 2;
/** Paper size: A3 Portrait */
public static int a3portrait = 3;
/** Paper size: A4 Portrait */
public static int a4portrait = 4;
/** Paper size: A5 Portrait */
public static int a5portrait = 5;
/** Paper size: A0 Landscape */
public static int a0landscape = 6;
/** Paper size: A1 Landscape */
public static int a1landscape = 7;
/** Paper size: A2 Landscape */
public static int a2landscape = 8;
/** Paper size: A3 Landscape */
public static int a3landscape = 9;
/** Paper size: A4 Landscape */
public static int a4landscape = 10;
/** Paper size: A5 Landscape */
public static int a5landscape = 11;
/** Paper size: US Letter Portrait */
public static int usletterportrait = 12;
/** Paper size: US Letter Landscape */
public static int usletterlandscape = 13;
/** Paper size: US Legal Portrait */
public static int uslegalportrait = 14;
/** Paper size: US Legal Landscape */
public static int uslegallandscape = 15;

/** Standard font: Times Roman */
public static int timesRoman = 0;
/** Standard font: Times Bold */
public static int timesBold = 1;
/** Standard font: Times Italic */
public static int timesItalic = 2;
/** Standard font: Times Bold Italic */
public static int timesBoldItalic = 3;
/** Standard font: Helvetica */
public static int helvetica = 4;
/** Standard font: Helvetica Bold */
public static int helveticaBold = 5;
/** Standard font: Helvetica Oblique */
public static int helveticaOblique = 6;
/** Standard font: Helvetica Bold Oblique */
public static int helveticaBoldOblique = 7;
/** Standard font: Courier */
public static int courier = 8;
/** Standard font: Courier Bold */
public static int courierBold = 9;
/** Standard font: Courier Oblique */
public static int courierOblique = 10;
/** Standard font: Courier Bold Oblique */
public static int courierBoldOblique = 11;

/** Position anchor: absolute centre. Takes two numbers, x and y. */
public static int posCentre = 0;
/** Position anchor: absolute left. Takes two numbers, x and y. */
public static int posLeft = 1;
/** Position anchor: absolute right. Takes two numbers, x and y. */
public static int posRight = 2;
/** Position anchor: the top centre of the page.
Takes one number - distance from top. Second number ignored. */
public static int top = 3;
/** Position anchor: the top left of the page.
Takes one numbers - distance from top left. Second number ignored. */
public static int topLeft = 4;
/** Position anchor: the top right of the page.
Takes one number - distance from top right. Second number ignored. */
public static int topRight = 5;
/** Position anchor: the left hand side of the page, halfway down.
Takes one number - distance from left middle. Second number ignored. */
public static int left = 6;
/** Position anchor: the bottom left of the page.
Takes one number - distance from bottom left. Second number ignored. */
public static int bottomLeft = 7;
/** Position anchor: the bottom middle of the page.
Takes one number - distance from bottom middle. Second number ignored. */
public static int bottom = 8;
/** Position anchor: the bottomm right of the page.
Takes one number - distance from bottom right. Second number ignored. */
public static int bottomRight = 9;
/** Position anchor: the right hand side of the page, halfway down.
Takes one number - distance from right middle. Second number ignored. */
public static int right = 10;
/** Position anchor: diagonal, bottom left to top right.
Takes no numbers. Both numbers ignored. */
public static int diagonal = 11;
/** Position anchor: diagonal, top left to bottom right.
Takes no numbers. Both numbers ignored. */
public static int reverseDiagonal = 12;
/** Justification: left */
public static int leftJustify = 0;
/** Justification: centre */
public static int centreJustify = 1;
/** Justification: right */
public static int rightJusitfy = 2;
