/* CHAPTER 14. Fonts. */

/** Retrieves font information. First, call {@link #startGetFontInfo(Pdf)
startGetFontInfo}. Now call {@link #numberFonts() numberFonts} to return
the number of fonts. For each font, call one or more of
{@link #getFontPage(int) getFontPage}, {@link #getFontName(int)
getFontName}, {@link #getFontType(int) getFontType}, and
{@link #getFontEncoding(int) getFontEncoding} giving a serial number
<code>0...n - 1</code> to return information. Finally, call
{@link #endGetFontInfo() endGetFontInfo} to clean up. */
public native void startGetFontInfo(Pdf pdf) throws CpdfError;

public native int numberFonts() throws CpdfError;

public native String getFontName(int serial) throws CpdfError;

public native int getFontPage(int serial) throws CpdfError;

public native String getFontType(int setial) throws CpdfError;

public native String getFontEncoding(int serial) throws CpdfError;

public native void endGetFontInfo() throws CpdfError;

/** Removes all font data from a file. */
public native void removeFonts(Pdf pdf) throws CpdfError;

/** Copies the given font
from the given page in the 'from' PDF to every page in the 'to' PDF. The
new font is stored under its font name.
@param from_pdf PDF document to copy from
@param to_pdf PDF document to copy to
@param range page range
@param pagenumber page number of the page to copy from
@param fontname font name */
public native void copyFont(Pdf from_pdf, Pdf to_pdf, Range range,
                            int pagenumber, String fontname)
    throws CpdfError;
