/* CHAPTER 0. Preliminaries */

/* The function cpdf_startup(argv) must be called before using the library.  */
void cpdf_startup(char **);

/* Return the version of the cpdflib library as a string */
char *cpdf_version();

/*
 * Some operations have a fast mode. The default is 'slow' mode, which works
 * even on old-fashioned files. For more details, see section 1.13 of the
 * CPDF manual. These functions set the mode globally.
 */
void cpdf_setFast();
void cpdf_setSlow();

/* Calling this function with a true argument sets embedding for the Standard
 * 14 fonts.  You must also set the directory to load them from with the next
 * function. Default value: false. */
void cpdf_embedStd14(int);

/* Set the directory to load Standard 14 fonts for embedding. */
void cpdf_embedStd14Dir(char *);

/*
 * Errors. cpdf_lastError and cpdf_lastErrorString hold information about the
 * last error to have occurred. They should be consulted after each call. If
 * cpdf_lastError is non-zero, there was an error, and cpdf_lastErrorString
 * gives details. If cpdf_lastError is zero, there was no error on the most
 * recent cpdf call.
 */
extern int cpdf_lastError;
extern char *cpdf_lastErrorString;

/* In some contexts, for example, .NET or JNI, constants in DLLs can be
 * difficult or impossible to access. we provide functions in addition. */
int cpdf_fLastError(void);
char *cpdf_fLastErrorString(void);

/* cpdf_clearError clears the current error state. */
void cpdf_clearError(void);

/*
 * cpdf_onExit is a debug function which prints some information about
 * resource usage. This can be used to detect if PDFs or ranges are being
 * deallocated properly. Contrary to its name, it may be run at any time.
 */
void cpdf_onExit(void);

