/* CHAPTER 13. Images. */

/* Get list of images. Call cpdf_startGetImages, which returns the total number
 * of images. Then serial numbers 0..<total number> - 1 are used to retreive
 * data. Finally, call cpdf_endGetImages to clean up. */
int cpdf_startGetImages(int);
int cpdf_getImageObjNum(int);
char *cpdf_getImagePages(int);
char *cpdf_getImageName(int);
int cpdf_getImageWidth(int);
int cpdf_getImageHeight(int);
int cpdf_getImageSize(int);
int cpdf_getImageBPC(int);
char *cpdf_getImageColSpace(int);
char *cpdf_getImageFilter(int);
void cpdf_endGetImages(void);

/*
 * Get image data, including resolution at all points of use. Call
 * cpdf_startGetImageResolution(pdf, min_required_resolution) will begin the
 * process of obtaining data on all image uses below min_required_resolution,
 * returning the total number. So, to return all image uses, specify a very
 * high min_required_resolution. Then, call the other functions giving a
 * serial number 0..<total number> - 1, to retrieve the data. Finally, call
 * cpdf_endGetImageResolution to clean up.
 */
int cpdf_startGetImageResolution(int, double);
int cpdf_getImageResolutionPageNumber(int);
char *cpdf_getImageResolutionImageName(int);
int cpdf_getImageResolutionXPixels(int);
int cpdf_getImageResolutionYPixels(int);
double cpdf_getImageResolutionXRes(int);
double cpdf_getImageResolutionYRes(int);
int cpdf_getImageResolutionObjNum(int);
void cpdf_endGetImageResolution(void);

/* Get image resolution data in JSON format */
void *cpdf_imageResolutionJSON(int, int *, float);

/* Get image data in JSON format */
void *cpdf_imagesJSON(int, int *);

