/* CHAPTER 17. Creating New PDFs */

/* cpdf_blankDocument(width, height, num_pages) creates a blank document with
 * pages of the given width (in points), height (in points), and number of
 * pages.
 */
int cpdf_blankDocument(double, double, int);

/*
 * cpdf_blankDocumentPaper(papersize, num_pages) makes a blank document given
 * a page size and number of pages.
 */
int cpdf_blankDocumentPaper(enum cpdf_papersize, int);

/* cpdf_textToPDF(w, h, font, fontsize, filename) typesets a UTF8 text file
 * ragged right on a page of size w * h in points in the given font and font
 * size. */
int cpdf_textToPDF(double, double, const char[], double, const char[]);

/* cpdf_textToPDFMemory(w, h, font, fontsize, data, length) typesets a UTF8 text
 * file ragged right on a page of size w * h in points in the given font and
 * font size. */
int cpdf_textToPDFMemory(double, double, const char[], double, void *, int);

/* cpdf_textToPDF(papersize, font, fontsize, filename) typesets a UTF8 text file
 * ragged right on a page of the given size in the given font and font size. */
int cpdf_textToPDFPaper(int, const char[], double, const char[]);

/* cpdf_textToPDFMemory(papersize font, fontsize, data, length) typesets a UTF8
 * text file ragged right on a page of the given size in the given font and
 * font size. */
int cpdf_textToPDFPaperMemory(int, const char[], double, void *, int);

/* cpdf_fromPNG(filename) builds a PDF from a non-interlaced non-transparent
 * PNG. */
int cpdf_fromPNG(const char[]);

/* cpdf_fromPNGMemory(data, length) builds a PDF from a non-interlaced
 * non-transparent PNG. */
int cpdf_fromPNGMemory(void *, int);

/* cpdf_fromJPEG(filename) builds a PDF from a JPEG. */
int cpdf_fromJPEG(const char[]);

/* cpdf_fromJPEGMemory(data, length) builds a PDF from a JPEG. */
int cpdf_fromJPEGMemory(void *, int);

