Loading the libpypcdf and libcpdf DLLs
--------------------------------------

Before using the library, you must load the ``libpycpdf`` and ``libcpdf`` DLLs.
This is achieved with the ``pycpdf.loadDLL`` function, given the filename or
full path of the ``libpycpdf`` DLL.

On Windows, you may have to call ``os.add_dll_directory`` first. On MacOS, you
may need to give the full path, and you may need to install ``libcpdf.so`` in a
standard location ``/usr/local/lib/``, or use the ``install_name_tool`` command
to tell ``libpycpdf.so`` where to find ``libcpdf.so``.

Conventions
-----------

Any function may raise the exception ``CPDFError``, carrying a string describing
the error.

A 'range' is a list of integers specifying page numbers. Page numbers start at
1. Range arguments are called `r`.

Text arguments and results are in UTF8.

Units are in PDF points (1/72 inch).

Angles are in degrees.


Built-in values
---------------

Paper sizes:

a0portrait a1portrait a2portrait a3portrait a4portrait a5portrait a0landscape
a1landscape a2landscape a3landscape a4landscape a5landscape usletterportrait
usletterlandscape uslegalportrait uslegallandscape

Permissions:

noEdit noPrint noCopy noAnnot noForms noExtract noAssemble noHqPrint

Encryption methods:

pdf40bit pdf128bit aes128bitfalse aes128bittrue aes256bitfalse aes256bittrue
aes256bitisofalse aes256bitisotrue

Positions:

Positions with two numbers in a tuple e.g (posLeft, 10.0, 20.0)

posCentre posLeft posRight

Positions with one number in a tuple e.g (top, 5.0)

top topLeft topRight left bottomLeft bottomRight right

Positions with no numbers e.g diagonal

diagonal reverseDiagonal

Fonts:

timesRoman timesBold timesItalic timesBoldItalic helvetica helveticaBold
helveticaOblique helveticaBoldOblique courier courierBold courierOblique
courierBoldOblique

Justification:

leftJustify centreJustify rightJustify

Page layouts:

singlePage oneColumn twoColumnLeft twoColumnRight twoPageLeft twoPageRight

Page modes:

useNone useOutlines useThumbs useOC useAttachments

Page label styles:

decimalArabic uppercaseRoman lowercaseRoman uppercaseLetters lowercaseLetters


# CHAPTER 0. Preliminaries

class Pdf:
    """The type of PDF documents."""

def loadDLL(f):
    """Load the libpycpdf DLL from a given file, and set up pycpdflib. Must be
    called prior to using any other function in the library."""

class CPDFError(Exception):
    """Any function may raise an exception CPDFError, carrying a string
    describing what went wrong."""

def lastError():
    """Return the last error. Not usually used directly, since pycpdflib
    functions raise exceptions."""

def lastErrorString():
    """Return the last error string. Not usually used directly, since pycpdflib
    functions raise exceptions."""

def checkerror():
    """Raise an exception if the last function call resulted in an error. Not
    used directly, since pycpdflib functions will raise the exception
    directly."""

def version():
    """Return the version number of the pycpdflib library."""

def setFast():
    """ Set fast mode. Some operations have a fast mode. The default is 'slow'
    mode, which works even on old-fashioned files. For more details, see
    section 1.13 of the CPDF manual. This function sets the mode globally. """

def setSlow():
    """ Set slow mode. Some operations have a fast mode. The default is 'slow'
    mode, which works even on old-fashioned files. For more details, see
    section 1.13 of the CPDF manual. This function sets the mode globally. """

def clearError():
    """ Clear the current error state. """

def onExit():
    """ A debug function which prints some information about
    resource usage. This can be used to detect if PDFs or ranges are being
    deallocated properly."""
