// CHAPTER 6. Bookmarks

/** Starts the bookmark retrieval process for a given PDF. */
function startGetBookmarkInfo(pdf)

/** Gets the number of bookmarks for the PDF given to startGetBookmarkInfo. */
function numberBookmarks()

/** Gets the bookmark level for the given bookmark (0...(n - 1)). */
function getBookmarkLevel(n)

/** Gets the bookmark target page for the given PDF (which must be the same
as the PDF passed to startSetBookmarkInfo) and bookmark (0...(n - 1)). */
function getBookmarkPage(pdf, n)

/** Returns the text of bookmark (0...(n - 1)). */
function getBookmarkText(n)

/** True if the bookmark is open. */
function getBookmarkOpenStatus(n)

/** Ends the bookmark retrieval process, cleaning up. */
function endGetBookmarkInfo()

/** Starts the bookmark setting process for n bookmarks. */
function startSetBookmarkInfo(n)

/** Set bookmark level for the given bookmark (0...(n - 1)). */
function setBookmarkLevel(a, b)

/** Sets the bookmark target page for the given PDF (which must be the same as
the PDF to be passed to endSetBookmarkInfo) and bookmark (0...(n - 1)). */
function setBookmarkPage(pdf, a, b)

/** Sets the open status of bookmark (0...(n - 1)). */
function setBookmarkOpenStatus(a, b)

/** Sets the text of bookmark (0...(n - 1)). */
function setBookmarkText(n, t)

/** Ends the bookmark setting process, writing the bookmarks to the given
PDF. */
function endSetBookmarkInfo(pdf)

/** Returns the bookmark data in JSON format. */
function getBookmarksJSON(pdf)

/** Sets the bookmarks from JSON bookmark data. */
function setBookmarksJSON(pdf, data)

/** Typesets a table of contents from existing bookmarks and prepends it to
the document. If bookmark is set, the table of contents gets its own
bookmark. */
function tableOfContents(pdf, font, fontsize, title, bookmark)
