// CHAPTER 8. Logos, Watermarks and Stamps
   
/** A stamping function with extra features. - isover true, pdf goes over pdf2,
isover false, pdf goes under pdf2 - scale_stamp_to_fit scales the stamp to fit
the page - pos gives the position to put the stamp - relative_to_cropbox: if
true, pos is relative to cropbox not mediabox. */
function stampOn(stamp_pdf, pdf, range)

/** Stamps stamp_pdf under all the pages in the document which are in the
range. The stamp is placed with its origin at the origin of the target
document. */
function stampUnder(stamp_pdf, pdf, range)

/** A stamping function with extra features. - isover true, pdf goes over
pdf2, isover false, pdf goes under pdf2 - scale_stamp_to_fit scales the
stamp to fit the page - pos gives the position to put the stamp -
relative_to_cropbox: if true, pos is relative to cropbox not mediabox. */
function stampExtended(pdf, pdf2, range, isover, scale_stamp_to_fit, position,
                       relative_to_cropbox)

/** Combines the PDFs page-by-page, putting each page of 'over' over each page
of 'under'. */
function combinePages(under, over)

/** Adds text to the pages in the given range. */
function addText(metrics, pdf, range, text, position, linespacing,
                 bates, font, fontsize, r, g, b, underneath, relative_to_cropbox,
                 outline, opacity, justification, midline, topline, filename,
                 linewidth, embed_fonts)

/** Adds text with most parameters default. */
function addTextSimple(pdf, range, text, position, font, fontsize)

/** Removes any text added by cpdf from the given pages. */
function removeText(pdf, range)

/** Returns the width of a given string in the given font in thousandths of a
point. */
function textWidth(font, text)

/** Adds page content before (if true) or after (if false) the existing
content to pages in the given range in the given PDF. */
function addContent(content, before, pdf, range)

/** Stamps stamp_pdf onto the pages in the given range in pdf as a shared Form
XObject. The name of the newly-created XObject is returned. */
function stampAsXObject(pdf, range, stamp_pdf)
