// CHAPTER 12. File Attachments
    
/** Attaches a file to the pdf. It is attached at document level. */
function attachFile(filename, pdf)

/** Attaches a file, given its file name, pdf, and the page number
to which it should be attached. */
function attachFileToPage(filename, pdf, pagenumber)

/** Attaches data from memory, just like attachFile. */
function attachFileFromMemory(data, filename, pdf)

/** Attaches to a page from memory, just like attachFileToPage. */
function attachFileToPageFromMemory(data, filename, pdf, pagenumber)

/** Removes all page- and document-level attachments from a document. */
function removeAttachedFiles(pdf)

/** Lists information about attachments. Call startGetAttachments(pdf) first,
then numberGetAttachments to find out how many there are. Then
getAttachmentName etc. to return each one 0...(n - 1). Finally, call
endGetAttachments to clean up. */
function startGetAttachments(pdf)

/** Lists information about attachments. Call startGetAttachments(pdf) first,
then numberGetAttachments to find out how many there are. Then
getAttachmentName etc. to return each one 0...(n - 1). Finally, call
endGetAttachments to clean up. */
function numberGetAttachments()

/** Gets the name of an attachment. */
function getAttachmentName(n)

/** Gets the page number. 0 = document level. */
function getAttachmentPage(n)

/** Gets the attachment data itself. */
function getAttachmentData(n)

/** Cleans up after getting attachments. */
function endGetAttachments()
