//CHAPTER 18. Miscellaneous

/** Removes images on the given pages, replacing them with crossed boxes if
'boxes' is true. */
function draft(pdf, range, boxes)

/** Removes all text from the given pages in a given document. */
function removeAllText(pdf, range)

/* Blackens all text on the given pages. */
function blackText(pdf, range)

/** Blackens all lines on the given pages. */
function blackLines(pdf, range)

/** Blackens all fills on the given pages. */
function blackFills(pdf, range)

/** Thickens every line less than min_thickness to min_thickness. Thickness
given in points. */
function thinLines(pdf, range, min_thickness)

/** Copies the /ID from one document to another. */
function copyId(pdf_from, pdf_to)

/** Removes a document's /ID. */
function removeId(pdf)

/** Sets the minor version number of a document. */
function setVersion(pdf, version)

/** Sets the full version number of a document. */
function setFullVersion(pdf, major, minor)

/** Removes any dictionary entry with the given key anywhere in the document. */
function removeDictEntry(pdf, key)

/** Removes any dictionary entry with the given key whose value matches the
given search term. */
function removeDictEntrySearch(pdf, key, searchterm)

/** Replaces the value associated with the given key. */
function replaceDictEntry(pdf, key, newval)

/** Replaces the value associated with the given key if the existing value
matches the search term. */
function replaceDictEntrySearch(pdf, key, newval, searchterm)

/** Removes all clipping from pages in the given range. */
function removeClipping(pdf, range)

/* Returns a JSON array containing any and all values associated with the
given key, and fills in its length. */
function getDictEntries(pdf, key)
