CHAPTER 18. Miscellaneous

Cpdf.draft(Cpdf.Pdf, List{Int32}, Boolean)

Removes images on the given pages, replacing them with crossed boxes if 'boxes'
is true.

Cpdf.removeAllText(Cpdf.Pdf, List{Int32})

Removes all text from the given pages in a given document.

Cpdf.blackText(Cpdf.Pdf, List{Int32})

Blackens all text on the given pages.

Cpdf.blackLines(Cpdf.Pdf, List{Int32})

Blackens all lines on the given pages.

Cpdf.blackFills(Cpdf.Pdf, List{Int32})

Blackens all fills on the given pages.

Cpdf.thinLines(Cpdf.Pdf, List{Int32}, Double)

Thickens every line less than min_thickness to min_thickness. Thickness given
in points.

Cpdf.copyId(Cpdf.Pdf, Cpdf.Pdf)

Copies the /ID from one document to another.

Cpdf.removeId(Cpdf.Pdf)

Removes a document's /ID.

Cpdf.setVersion(Cpdf.Pdf, Int32)

Sets the minor version number of a document.

Cpdf.setFullVersion(Cpdf.Pdf, Int32, Int32)

Sets the full version number of a document.

Cpdf.removeDictEntry(Cpdf.Pdf, String)

Removes any dictionary entry with the given key anywhere in the document.

Cpdf.removeDictEntrySearch(Cpdf.Pdf, String, String)

Removes any dictionary entry with the given key whose value matches the given
search term.

Cpdf.replaceDictEntry(Cpdf.Pdf, String, String)

Replaces the value associated with the given key.

Cpdf.replaceDictEntrySearch(Cpdf.Pdf, String, String, String)

Replaces the value associated with the given key if the existing value matches
the search term.

Cpdf.removeClipping(Cpdf.Pdf, List{Int32})

Removes all clipping from pages in the given range.

Cpdf.getDictEntries(Cpdf.Pdf, String)

Returns a JSON array containing any and all values associated with the given
key, and fills in its length.
