# CHAPTER 9. Multipage facilities

def twoUp(pdf):
    """Impose a document two up by retaining the existing page size, scaling
    pages down."""

def twoUpStack(pdf):
    """Impose a document two up by doubling the page size, to fit two pages on
    one."""

def impose(pdf, x, y, fit, columns, rtl, btt, center, margin, spacing, linewidth):
    """Impose a PDF. There are two modes: imposing x * y, or imposing to fit a
    page of size x * y. This is controlled by fit. Columns imposes by columns
    rather than rows. rtl is right-to-left, btt bottom-to-top. Center is unused
    for now. Margin is the margin around the output, spacing the spacing
    between imposed inputs."""

def chop(pdf, r, x, y, columns, rtl, btt):
    """Chop each page in the range into x * y pieces. If columns is set, the
    pieces go by columns instead of rows. If rtl is set, the pieces are taken
    right-to-left. If btt is set, the pieces are taken from bottom to top. """

def chopH(pdf, r, columns, y):
    """Chop each page in the range horizontally at position y. If columns is
    set, the pieces are arranged in reverse order. """

def chopV(pdf, r, columns, x):
    """Chop each page in the range vertically at position x. If columns is
    set, the pieces are arranged in reverse order. """

def padBefore(pdf, r):
    """Adds a blank page before each page in the given range."""

def padAfter(pdf, r):
    """Adds a blank page after each page in the given range."""

def padEvery(pdf, n):
    """Adds a blank page after every n pages."""

def padMultiple(pdf, n):
    """Adds pages at the end to pad the file to a multiple of n pages in
    length."""

def padMultipleBefore(pdf, n):
    """Adds pages at the beginning to pad the file to a multiple of n pages in
    length."""
