# CHAPTER 18. Drawing on PDFs

def drawBegin():
    """Sets up the drawing process. It must be called before any other draw*
    function."""

def drawEnd(pdf, r):
    """Commits the drawing to the given PDF on pages in the given range."""

def drawEndExtended(pdf, r, underneath, bates, filename):
    """The same as drawEnd, but provides the special parameters which may be
    required when using drawSText."""

def drawRect(x, y, w, h):
    """Add a rectangle to the current path."""

def drawTo(x, y):
    """Move the current point to (x, y)."""

def drawLine(x, y):
    """Adds a line from the current point to (x, y) to the current path."""

def drawBez(x1, y1, x2, y2, x3, y3):
    """Adds a Bezier curve to the current path."""

def drawBez23(x2, y2, x3, y3):
    """Adds a Bezier curve twith (x1, y1) = current point."""

def drawBez13(x1, y1, x3, y3):
    """Adds a Bezier curve with (x3, y3) = new current point."""

def drawCircle(x, y, r):
    """Adds a circle to the current path."""

def drawStroke():
    """Stroke the current path and clear it."""

def drawFill():
    """Fills the current path with a non-zero winding rule, and clears it. """

def drawFillEo():
    """Fills the current path with an even-odd winding rule, and clears it. """

def drawStrokeFill():
    """Fills and then strokes the current path with a non-zero winding rule,
    and clears it. """

def drawStrokeFillEo():
    """Fills and then strokes the current path with an even-odd winding rule,
    and clears it. """

def drawClose():
    """Closes the current path by appending a straight line segment from the
    current point to the starting point of the subpath. """

def drawClip():
    """Uses the current path as a clipping region, using the non-zero winding
    rule. """

def drawClipEo():
    """Uses the current path as a clipping region, using the even-odd winding
    rule. """

def drawStrokeColGrey(g):
    """Changes to a greyscale stroke colourspace and sets the stroke colour.
    """

def drawStrokeColRGB(r, g, b):
    """Changes to an RGB stroke colourspace and sets the stroke colour. """

def drawStrokeColCYMK(c, y, m, k):
    """Changes to a CYMK stroke colourspace and sets the stroke colour. """

def drawFillColGrey(g):
    """Changes to a greyscale fill colourspace and sets the fill colour. """

def drawFillColRGB(r, g, b):
    """Changes to an RGB fill colourspace and sets the fill colour. """

def drawFillColCYMK(c, y, m, k):
    """Changes to a CYMK fill colourspace and sets the fill colour. """

def drawThick(thickness):
    """Sets the line thickness."""

def drawCap(captype):
    """Sets the line cap."""

def drawJoin(jointype):
    """Sets the line join type"""

def drawMiter(miter):
    """Sets the miter limit."""

def drawDash(description):
    """Sets the line dash style"""

def drawPush():
    """Saves the current graphics state on the stack. """

def drawPop():
    """Restores the graphics state from the stack. """

def drawMatrix(a, b, c, d, e, f):
    """Appends the given matrix to the Current Transformation Matrix. """

def drawMTrans(tx, ty):
    """Appends a translation by (tx, ty) to the Current Transformation Matrix.
    """

def drawMRot(x, y, a):
    """Appends a rotation by a around (a, y) to the Current Transformation
    Matrix. """

def drawMScale(x, y, sx, sy):
    """Appends a scaling by (sx, sy) around (x, y) to the Current
    Transformation Matrix. """

def drawMShearX(x, y, a):
    """Appends an X shearing of angle a around (x, y) to the Current
    Transformation Matrix. """

def drawMShearY(x, y, a):
    """Appends an X shearing of angle a around (x, y) to the Current
    Transformation Matrix. """

def drawXObjBBox(x, y, w, h):
    """Sets the XObject bounding box. """

def drawXObj(name):
    """Begins the storing of an XObject. """

def drawEndXObj():
    """Ends the storing of an XObject."""

def drawUse(name):
    """Uses the named XObject. """

def drawJPEG(name, filename):
    """Loads a JPEG from the given file, storing it under the given name. """

def drawJPEGMemory(name, data):
    """Loads a JPEG from the given bytearray, storing it under the given name.
    """

def drawPNG(name, filename):
    """Loads a non-interlaced non-transparent PNG from the given file, storing
    it under the given name. """

def drawPNGMemory(name, data):
    """Loads a non-interlaced non-transparent PNG from the given bytearray,
    storing it under the given name. """

def drawImage(name):
    """Draws a stored image. To draw at the expected size, it is required to
    scale the Current Transformation Matrix by the width and height of the
    image. """

def drawFillOpacity(n):
    """Sets the fill opacity."""

def drawStrokeOpacity(n):
    """Sets the stroke opacity."""

def drawBT():
    """Begins a text section."""

def drawET():
    """Ends a text section."""

def drawFont(name):
    """Sets the font."""

def drawFontSize(n):
    """Sets the font size."""

def drawText(text):
    """Draws text."""

def drawSText(text):
    """draws text with %Specials. You may need to use cpdf_drawEndExtended
    instead of cpdf_drawEnd later, to provide the extra information required.
    """

def drawLeading(n):
    """Sets the leading."""

def drawCharSpace(n):
    """Sets the character spacing."""

def drawWordSpace(n):
    """Sets the word spacing."""

def drawTextScale(n):
    """Sets the text scaling."""

def drawRenderMode(n):
    """Sets the text rendering mode."""

def drawRise(n):
    """Sets the text rise."""

def drawNL():
    """Moves to the next line. """

def drawNewPage():
    """Moves to the next page, creating it if necessary, and setting the range
    to just that new page. """
