/* CHAPTER 11. Document Information and Metadata */

/*
 * cpdf_isLinearized(filename) finds out if a document is linearized as
 * quickly as possible without loading it.
 */
int cpdf_isLinearized(const char[]);

/* cpdf_getVersion(pdf) returns the minor version number of a document. */
int cpdf_getVersion(int);

/* cpdf_getMajorVersion(pdf) returns the minor version number of a document. */
int cpdf_getMajorVersion(int);

/* cpdf_getTitle(pdf) returns the title of a document. */
char *cpdf_getTitle(int);

/* cpdf_getAuthor(pdf) returns the author of a document. */
char *cpdf_getAuthor(int);

/* cpdf_getSubject(pdf) returns the subject of a document. */
char *cpdf_getSubject(int);

/* cpdf_getKeywords(pdf) returns the keywords of a document. */
char *cpdf_getKeywords(int);

/* cpdf_getCreator(pdf) returns the creator of a document. */
char *cpdf_getCreator(int);

/* cpdf_getProducer(pdf) returns the producer of a document. */
char *cpdf_getProducer(int);

/* cpdf_getCreationDate(pdf) returns the creation date of a document. */
char *cpdf_getCreationDate(int);

/* cpdf_getModificationDate(pdf) returns the modification date of a document. */
char *cpdf_getModificationDate(int);

/* cpdf_getTitleXMP(pdf) returns the XMP title of a document. */
char *cpdf_getTitleXMP(int);

/* cpdf_getAuthorXMP(pdf) returns the XMP author of a document. */
char *cpdf_getAuthorXMP(int);

/* cpdf_getSubjectXMP(pdf) returns the XMP subject of a document. */
char *cpdf_getSubjectXMP(int);

/* cpdf_getKeywordsXMP(pdf) returns the XMP keywords of a document. */
char *cpdf_getKeywordsXMP(int);

/* cpdf_getCreatorXMP(pdf) returns the XMP creator of a document. */
char *cpdf_getCreatorXMP(int);

/* cpdf_getProducerXMP(pdf) returns the XMP producer of a document. */
char *cpdf_getProducerXMP(int);

/* cpdf_getCreationDateXMP(pdf) returns the XMP creation date of a document. */
char *cpdf_getCreationDateXMP(int);

/*
 * cpdf_getModificationDateXMP(pdf) returns the XMP modification date of a
 * document.
 */
char *cpdf_getModificationDateXMP(int);

/* cpdf_setTitle(pdf) sets the title of a document. */
void cpdf_setTitle(int, const char[]);

/* cpdf_setAuthor(pdf) sets the author of a document. */
void cpdf_setAuthor(int, const char[]);

/* cpdf_setSubject(pdf) sets the subject of a document. */
void cpdf_setSubject(int, const char[]);

/* cpdf_setKeywords(pdf) sets the keywords of a document. */
void cpdf_setKeywords(int, const char[]);

/* cpdf_setCreator(pdf) sets the creator of a document. */
void cpdf_setCreator(int, const char[]);

/* cpdf_setProducer(pdf) sets the producer of a document. */
void cpdf_setProducer(int, const char[]);

/* cpdf_setCreationDate(pdf) sets the creation date of a document. */
void cpdf_setCreationDate(int, const char[]);

/* cpdf_setModificationDate(pdf) sets the modifcation date of a document. */
void cpdf_setModificationDate(int, const char[]);

/* cpdf_setTitleXMP(pdf) sets the XMP title of a document. */
void cpdf_setTitleXMP(int, const char[]);

/* cpdf_setAuthorXMP(pdf) sets the XMP author of a document. */
void cpdf_setAuthorXMP(int, const char[]);

/* cpdf_setSubjectXMP(pdf) sets the XMP subject of a document. */
void cpdf_setSubjectXMP(int, const char[]);

/* cpdf_setKeywordsXMP(pdf) sets the XMP keywords of a document. */
void cpdf_setKeywordsXMP(int, const char[]);

/* cpdf_setCreatorXMP(pdf) sets the XMP creator of a document. */
void cpdf_setCreatorXMP(int, const char[]);

/* cpdf_setProducerXMP(pdf) sets the XMP producer of a document. */
void cpdf_setProducerXMP(int, const char[]);

/* cpdf_setCreationDateXMP(pdf) sets the XMP creation date of a document. */
void cpdf_setCreationDateXMP(int, const char[]);

/*
 * cpdf_setModificationDateXMP(pdf) sets the XMP modification date of a
 * document.
 */
void cpdf_setModificationDateXMP(int, const char[]);

/*
 * Dates: Month 1-31, day 1-31, hours (0-23), minutes (0-59), seconds (0-59),
 * hour_offset is the offset from UT in hours (-23 to 23); minute_offset is
 * the offset from UT in minutes (-59 to 59).
 */

/*
 * cpdf_getDateComponents(datestring, year, month, day, hour, minute, second,
 * hour_offset, minute_offset) returns the components from a PDF date string.
 */
void cpdf_getDateComponents(const char[], int *, int *, int *, int *, int *,
                            int *, int *, int *);

/*
 * cpdf_dateStringOfComponents(year, month, day, hour, minute, second,
 * hour_offset, minute_offset) builds a PDF date string from individual
 * components.
 */
char *cpdf_dateStringOfComponents(int, int, int, int, int, int, int, int);

/*
 * cpdf_getPageRotation(pdf, pagenumber) gets the viewing rotation for a
 * given page.
 */
int cpdf_getPageRotation(int, int);

/*
 * cpdf_hasBox(pdf, pagenumber, boxname) returns true, if that page has the
 * given box. E.g "/CropBox".
 */
int cpdf_hasBox(int, int, const char[]);

/*
 * These functions get a box given the document, page number, min x, max x,
 * min y, max y in points. Only succeeds if such a box exists, as checked by
 * cpdf_hasBox.
 */
void cpdf_getMediaBox(int, int, double *, double *, double *, double *);
void cpdf_getCropBox(int, int, double *, double *, double *, double *);
void cpdf_getTrimBox(int, int, double *, double *, double *, double *);
void cpdf_getArtBox(int, int, double *, double *, double *, double *);
void cpdf_getBleedBox(int, int, double *, double *, double *, double *);

/*
 * These functions set a box given the document, page range, min x, max x,
 * min y, max y in points.
 */
void cpdf_setMediabox(int, int, double, double, double, double);
void cpdf_setCropBox(int, int, double, double, double, double);
void cpdf_setTrimBox(int, int, double, double, double, double);
void cpdf_setArtBox(int, int, double, double, double, double);
void cpdf_setBleedBox(int, int, double, double, double, double);

/* cpdf_markTrapped(pdf) marks a document as trapped. */
void cpdf_markTrapped(int);

/* cpdf_markUntrapped(pdf) marks a document as untrapped. */
void cpdf_markUntrapped(int);

/* cpdf_markTrappedXMP(pdf) marks a document as trapped in XMP metadata. */
void cpdf_markTrappedXMP(int);

/* cpdf_markUntrappedXMP(pdf) marks a document as untrapped in XMP metadata. */
void cpdf_markUntrappedXMP(int);

/* Document Layouts. */
enum cpdf_layout {
  cpdf_singlePage,
  cpdf_oneColumn,
  cpdf_twoColumnLeft,
  cpdf_twoColumnRight,
  cpdf_twoPageLeft,
  cpdf_twoPageRight
};

/* cpdf_setPageLayout(pdf, layout) sets the page layout for a document. */
void cpdf_setPageLayout(int, enum cpdf_layout);

/* Document page modes. */
enum cpdf_pageMode {
  cpdf_useNone,
  cpdf_useOutlines,
  cpdf_useThumbs,
  cpdf_useOC,
  cpdf_useAttachments
};

/* cpdf_setPageMode(pdf, mode) sets the page mode for a document. */
void cpdf_setPageMode(int, enum cpdf_pageMode);

/* cpdf_hideToolbar(pdf, flag) sets the hide toolbar flag. */
void cpdf_hideToolbar(int, int);

/* cpdf_hideMenubar(pdf, flag) sets the hide menu bar flag. */
void cpdf_hideMenubar(int, int);

/* cpdf_hideWindowUi(pdf, flag) sets the hide window UI flag. */
void cpdf_hideWindowUi(int, int);

/* cpdf_fitWindow(pdf, flag) sets the fit window flag. */
void cpdf_fitWindow(int, int);

/* cpdf_centerWindow(pdf, flag) sets the center window flag. */
void cpdf_centerWindow(int, int);

/* cpdf_displayDocTitle(pdf, flag) sets the display doc title flag. */
void cpdf_displayDocTitle(int, int);

/* cpdf_openAtPage(pdf, fit, pagenumber) sets the PDF to open, possibly with
 * zoom-to-fit, at the given page number. */
void cpdf_openAtPage(int, int, int);

/*
 * cpdf_setMetadataFromFile(pdf, filename) set the XMP metadata of a
 * document, given a file name.
 */
void cpdf_setMetadataFromFile(int, const char[]);

/*
 * cpdf_setMetadataFromByteArray(pdf, data, length) set the XMP metadata from
 * an array of bytes.
 */
void cpdf_setMetadataFromByteArray(int, void *, int);

/*
 * cpdf_getMetadata(pdf, &length) returns the XMP metadata and fills in
 * length.
 */
void *cpdf_getMetadata(int, int *);

/* cpdf_removeMetadata(pdf) removes the XMP metadata from a document. */
void cpdf_removeMetadata(int);

/*
 * cpdf_createMetadata(pdf) builds fresh metadata as best it can from
 * existing metadata in the document.
 */
void cpdf_createMetadata(int);

/*
 * cpdf_setMetadataDate(pdf, date) sets the metadata date for a PDF. The date
 * is given in PDF date format -- cpdf will convert it to XMP format. The
 * date 'now' means now.
 */
void cpdf_setMetadataDate(int, const char[]);

/* Styles of page label */
enum cpdf_pageLabelStyle {
  cpdf_decimalArabic,    /* 1, 2, 3... */
  cpdf_uppercaseRoman,   /* I, II, III... */
  cpdf_lowercaseRoman,   /* i, ii, iii... */
  cpdf_uppercaseLetters, /* A, B, C... */
  cpdf_lowercaseLetters  /* a, b, c... */
};

/*
 * Add page labels.
 *
 * cpdf_addPageLabels(pdf, style, prefix, offset, range, progress)
 *
 * The prefix is prefix text for each label. The range is the page range the
 * labels apply to. Offset can be used to shift the numbering up or down.
 */
void cpdf_addPageLabels(int, enum cpdf_pageLabelStyle, const char[], int, int,
                        int);

/* cpdf_removePageLabels(pdf) removes the page labels from the document. */
void cpdf_removePageLabels(int);

/*
 * cpdf_getPageLabelStringForPage(pdf, page number) calculates the full label
 * string for a given page, and returns it.
 */
char *cpdf_getPageLabelStringForPage(int, int);

/*
 * Get page label data. Call cpdf_startGetPageLabels to find out how many
 * there are, then use these serial numbers to get the style, prefix, offset
 * and start value (note not a range). Call cpdf_endGetPageLabels to clean up.
 *
 * For example, a document might have five pages of introduction with roman
 * numerals, followed by the rest of the pages in decimal arabic, numbered from
 * one:
 *
 * labelstyle = LowercaseRoman
 * labelprefix = ""
 * startpage = 1
 * startvalue = 1
 *
 * labelstyle = DecimalArabic
 * labelprefix = ""
 * startpage = 6
 * startvalue = 1
 */
int cpdf_startGetPageLabels(int);
enum cpdf_pageLabelStyle cpdf_getPageLabelStyle(int);
char *cpdf_getPageLabelPrefix(int);
int cpdf_getPageLabelOffset(int);
int cpdf_getPageLabelRange(int);
void cpdf_endGetPageLabels();

