CHAPTER 3. Pages

Cpdf.scalePages(Cpdf.Pdf, List{Int32}, Double, Double)

Scales the page dimensions
and content by the given scale, about (0, 0). Other boxes (crop etc. are
altered as appropriate)

Cpdf.scaleToFit(Cpdf.Pdf, List{Int32}, Double, Double, Double)

Scales the content to fit
new page dimensions (width x height) multiplied by scale (typically 1.0).
Other boxes (crop etc. are altered as appropriate)

Cpdf.Papersize

Built-in paper sizes

Cpdf.Papersize.A0portrait

A0 Portrait paper

Cpdf.Papersize.A1portrait

A1 Portrait paper

Cpdf.Papersize.A2portrait

A2 Portrait paper

Cpdf.Papersize.A3portrait

A3 Portrait paper

Cpdf.Papersize.A4portrait

A4 Portrait paper

Cpdf.Papersize.A5portrait

A5 Portrait paper

Cpdf.Papersize.A0landscape

A0 Landscape paper

Cpdf.Papersize.A1landscape

A1 Landscape paper

Cpdf.Papersize.A2landscape

A2 Landscape paper

Cpdf.Papersize.A3landscape

A3 Landscape paper

Cpdf.Papersize.A4landscape

A4 Landscape paper

Cpdf.Papersize.A5landscape

A5 Landscape paper

Cpdf.Papersize.Usletterportrait

US Letter Portrait paper

Cpdf.Papersize.Usletterlandscape

US Letter Landscape paper

Cpdf.Papersize.Uslegalportrait

US Legal Portrait paper

Cpdf.Papersize.Uslegallandscape

US Legal Landscape paper

Cpdf.scaleToFitPaper(Cpdf.Pdf, List{Int32}, Cpdf.Papersize, Double)

Scales the page content
to fit the given page size, possibly multiplied by scale (typically 1.0)

Cpdf.Anchor

Position anchors

Cpdf.Anchor.PosCentre

Absolute centre

Cpdf.Anchor.PosLeft

Absolute left

Cpdf.Anchor.PosRight

Absolute right

Cpdf.Anchor.Top

The top centre of the page

Cpdf.Anchor.TopLeft

The top left of the page

Cpdf.Anchor.TopRight

The top right of the page

Cpdf.Anchor.Left

The left hand side of the page, halfway down

Cpdf.Anchor.BottomLeft

The bottom left of the page

Cpdf.Anchor.Bottom

The bottom middle of the page

Cpdf.Anchor.BottomRight

The bottom right of the page

Cpdf.Anchor.Right

The right hand side of the page, halfway down

Cpdf.Anchor.Diagonal

Diagonal, bottom left to top right

Cpdf.Anchor.ReverseDiagonal

Diagonal, top left to bottom right

Cpdf.Position

Cpdf.Position.anchor

Position anchor

Cpdf.Position.coord1

Parameter one

Cpdf.Position.coord2

Parameter two

Cpdf.Position.#ctor(Cpdf.Anchor)

Build a position with zero parameters

Cpdf.Position.#ctor(Cpdf.Anchor, Double)

Build a position with one parameter

Cpdf.Position.#ctor(Cpdf.Anchor, Double, Double)

Build a position with two parameters

Cpdf.scaleContents(Cpdf.Pdf, List{Int32}, Cpdf.Position, Double)

Scales the contents of the
pages in the range about the point given by the position, by the
scale given.

Cpdf.shiftContents(Cpdf.Pdf, List{Int32}, Double, Double)

Shifts the content of the pages in
the range.

Cpdf.rotate(Cpdf.Pdf, List{Int32}, Int32)

Changes the viewing rotation to an
absolute value. Appropriate rotations are 0, 90, 180, 270.

Cpdf.rotateBy(Cpdf.Pdf, List{Int32}, Int32)

Rotates the content about the
centre of the page by the given number of degrees, in a clockwise
direction.

Cpdf.rotateContents(Cpdf.Pdf, List{Int32}, Double)

Rotates the content about the
centre of the page by the given number of degrees, in a clockwise
direction.

Cpdf.upright(Cpdf.Pdf, List{Int32})

Changes the viewing rotation of the pages in the
range, counter-rotating the dimensions and content such that there is no
visual change.

Cpdf.hFlip(Cpdf.Pdf, List{Int32})

Flips horizontally the pages in the range.

Cpdf.vFlip(Cpdf.Pdf, List{Int32})

Flips vertically the pages in the range.

Cpdf.crop(Cpdf.Pdf, List{Int32}, Double, Double, Double, Double)

Crops a page, replacing any existing
crop box. The dimensions are in points.

Cpdf.removeCrop(Cpdf.Pdf, List{Int32})

Removes any crop box from pages in the range.

Cpdf.removeTrim(Cpdf.Pdf, List{Int32})

Removes any trim box from pages in the range.

Cpdf.removeArt(Cpdf.Pdf, List{Int32})

Removes any art box from pages in the range.

Cpdf.removeBleed(Cpdf.Pdf, List{Int32})

Removes any bleed box from pages in the range.

Cpdf.trimMarks(Cpdf.Pdf, List{Int32})

Adds trim marks to the given pages, if the
trimbox exists.

Cpdf.showBoxes(Cpdf.Pdf, List{Int32})

Shows the boxes on the given pages, for debug.

Cpdf.hardBox(Cpdf.Pdf, List{Int32}, String)

Makes a given box a 'hard box' i.e clips it explicitly.

Cpdf.dummych4

