CHAPTER 6. Bookmarks

Cpdf.startGetBookmarkInfo(Cpdf.Pdf)

Starts the bookmark retrieval process for a given PDF.

Cpdf.numberBookmarks

Gets the number of bookmarks for the PDF given to startGetBookmarkInfo.

Cpdf.getBookmarkLevel(Int32)

Gets the bookmark level for the given bookmark (0...(n - 1)).

Cpdf.getBookmarkPage(Cpdf.Pdf, Int32)

Gets the bookmark target page for the given PDF (which must be the same as the
PDF passed to startSetBookmarkInfo) and bookmark (0...(n - 1)).

Cpdf.getBookmarkText(Int32)

Returns the text of bookmark (0...(n - 1)).

Cpdf.getBookmarkOpenStatus(Int32)

True if the bookmark is open.

Cpdf.endGetBookmarkInfo

Ends the bookmark retrieval process, cleaning up.

Cpdf.startSetBookmarkInfo(Int32)

Starts the bookmark setting process for n bookmarks.

Cpdf.setBookmarkLevel(Int32, Int32)

Set bookmark level for the given bookmark (0...(n - 1)).

Cpdf.setBookmarkPage(Cpdf.Pdf, Int32, Int32)

Sets the bookmark target page for the given PDF (which must be the same as the
PDF to be passed to endSetBookmarkInfo) and bookmark (0...(n - 1)).

Cpdf.setBookmarkOpenStatus(Int32, Boolean)

Sets the open status of bookmark (0...(n - 1)).

Cpdf.setBookmarkText(Int32, String)

Sets the text of bookmark (0...(n - 1)).

Cpdf.endSetBookmarkInfo(Cpdf.Pdf)

Ends the bookmark setting process, writing the bookmarks to the given PDF.

Cpdf.getBookmarksJSON(Cpdf.Pdf)

Returns the bookmark data in JSON format.

Cpdf.setBookmarksJSON(Cpdf.Pdf, Byte[])

Sets the bookmarks from JSON bookmark data.

Cpdf.tableOfContents(Cpdf.Pdf, Cpdf.Font, Double, String, Boolean)

Typesets a table of contents from existing bookmarks and prepends it to the
document. If bookmark is set, the table of contents gets its own bookmark.
