CHAPTER 8. Logos, Watermarks and Stamps

Cpdf.stampOn(Cpdf.Pdf, Cpdf.Pdf, List{Int32})


Stamps stamp_pdf on top of all the
pages in the document which are in the range. The stamp is placed with its
origin at the origin of the target document.


Cpdf.stampUnder(Cpdf.Pdf, Cpdf.Pdf, List{Int32})


Stamps stamp_pdf under all the
pages in the document which are in the range. The stamp is placed with its
origin at the origin of the target document.


Cpdf.stampExtended(Cpdf.Pdf, Cpdf.Pdf, List{Int32}, Boolean, Boolean, Cpdf.Position, Boolean)


A stamping function with extra features. - isover
true, pdf goes over pdf2, isover false, pdf goes under pdf2 -
scale_stamp_to_fit scales the stamp to fit the page - pos gives the
position to put the stamp - relative_to_cropbox: if true, pos is relative
to cropbox not mediabox.


Cpdf.combinePages(Cpdf.Pdf, Cpdf.Pdf)


Combines the PDFs page-by-page, putting
each page of 'over' over each page of 'under'.


Cpdf.Font

Standard fonts

Cpdf.Font.TimesRoman

Times Roman

Cpdf.Font.TimesBold

Times Bold

Cpdf.Font.TimesItalic

Times Italic

Cpdf.Font.TimesBoldItalic

Times Bold Italic

Cpdf.Font.Helvetica

Helvetica

Cpdf.Font.HelveticaBold

Helvetica Bold

Cpdf.Font.HelveticaOblique

Helvetica Oblique

Cpdf.Font.HelveticaBoldOblique

Helvetica Bold Oblique

Cpdf.Font.Courier

Courier

Cpdf.Font.CourierBold

Courier Bold

Cpdf.Font.CourierOblique

Courier Oblique

Cpdf.Font.CourierBoldOblique

Courier Bold Oblique

Cpdf.Justification

Justifications

Cpdf.Justification.LeftJustify

Left justify

Cpdf.Justification.CentreJustify

Centre justify

Cpdf.Justification.RightJustify

Right justify

Cpdf.addText(Boolean, Cpdf.Pdf, List{Int32}, String, Cpdf.Position, Double, Int32, Cpdf.Font, Double, Double, Double, Double, Boolean, Boolean, Boolean, Double, Cpdf.Justification, Boolean, Boolean, String, Double, Boolean)


Adds text to the pages in the given range.


Cpdf.addTextSimple(Cpdf.Pdf, List{Int32}, String, Cpdf.Position, Cpdf.Font, Double)


Adds text with most parameters default.


Cpdf.removeText(Cpdf.Pdf, List{Int32})


Removes any text added by cpdf from the
given pages.


Cpdf.textWidth(Cpdf.Font, String)


Returns the width of a given string in the given font in thousandths of a
point.


Cpdf.addContent(String, Boolean, Cpdf.Pdf, List{Int32})


Adds page content before (if
true) or after (if false) the existing content to pages in the given range
in the given PDF.


Cpdf.stampAsXObject(Cpdf.Pdf, List{Int32}, Cpdf.Pdf)


Stamps stamp_pdf onto the pages
in the given range in pdf as a shared Form XObject. The name of the
newly-created XObject is returned.


Cpdf.dummych9

