CHAPTER 11. Document Information and Metadata

Cpdf.isLinearized(String)


Finds out if a document is linearized as
quickly as possible without loading it.


Cpdf.getVersion(Cpdf.Pdf)


Returns the minor version number of a document.


Cpdf.getMajorVersion(Cpdf.Pdf)


Returns the minor version number of a document.


Cpdf.getTitle(Cpdf.Pdf)


Returns the title of a document.


Cpdf.getAuthor(Cpdf.Pdf)


Returns the author of a document.


Cpdf.getSubject(Cpdf.Pdf)


Returns the subject of a document.


Cpdf.getKeywords(Cpdf.Pdf)


Returns the keywords of a document.


Cpdf.getCreator(Cpdf.Pdf)


Returns the creator of a document.


Cpdf.getProducer(Cpdf.Pdf)


Returns the producer of a document.


Cpdf.getCreationDate(Cpdf.Pdf)


Returns the creation date of a document.


Cpdf.getModificationDate(Cpdf.Pdf)


Returns the modification date of a document.


Cpdf.getTitleXMP(Cpdf.Pdf)


Returns the XMP title of a document.


Cpdf.getAuthorXMP(Cpdf.Pdf)


Returns the XMP author of a document.


Cpdf.getSubjectXMP(Cpdf.Pdf)


Returns the XMP subject of a document.


Cpdf.getKeywordsXMP(Cpdf.Pdf)


Returns the XMP keywords of a document.


Cpdf.getCreatorXMP(Cpdf.Pdf)


Returns the XMP creator of a document.


Cpdf.getProducerXMP(Cpdf.Pdf)


Returns the XMP producer of a document.


Cpdf.getCreationDateXMP(Cpdf.Pdf)


Returns the XMP creation date of a document.


Cpdf.getModificationDateXMP(Cpdf.Pdf)


Returns the XMP modification date of a document.


Cpdf.setTitle(Cpdf.Pdf, String)


Sets the title of a document.


Cpdf.setAuthor(Cpdf.Pdf, String)


Sets the author of a document.


Cpdf.setSubject(Cpdf.Pdf, String)


Sets the subject of a document.


Cpdf.setKeywords(Cpdf.Pdf, String)


Sets the keywords of a document.


Cpdf.setCreator(Cpdf.Pdf, String)


Sets the creator of a document.


Cpdf.setProducer(Cpdf.Pdf, String)


Sets the producer of a document.


Cpdf.setCreationDate(Cpdf.Pdf, String)


Sets the creation date of a document.


Cpdf.setModificationDate(Cpdf.Pdf, String)


Sets the modification date of a document.


Cpdf.setTitleXMP(Cpdf.Pdf, String)


Sets the XMP title of a document.


Cpdf.setAuthorXMP(Cpdf.Pdf, String)


Sets the XMP author of a document.


Cpdf.setSubjectXMP(Cpdf.Pdf, String)


Sets the XMP subject of a document.


Cpdf.setKeywordsXMP(Cpdf.Pdf, String)


Sets the XMP keywords of a document.


Cpdf.setCreatorXMP(Cpdf.Pdf, String)


Sets the XMP creator of a document.


Cpdf.setProducerXMP(Cpdf.Pdf, String)


Sets the XMP producer of a document.


Cpdf.setCreationDateXMP(Cpdf.Pdf, String)


Sets the XMP creation date of a document.


Cpdf.setModificationDateXMP(Cpdf.Pdf, String)


Sets the XMP modification date of a document.


Cpdf.getDateComponents(String, Int32@, Int32@, Int32@, Int32@, Int32@, Int32@, Int32@, Int32@)


Returns the components from a PDF date string.


Cpdf.dateStringOfComponents(Int32, Int32, Int32, Int32, Int32, Int32, Int32, Int32)


Builds a PDF date string from individual
components.


Cpdf.getPageRotation(Cpdf.Pdf, Int32)


Gets the viewing rotation for a
given page.


Cpdf.hasBox(Cpdf.Pdf, Int32, String)


Returns true, if that page has the
given box. E.g "/CropBox".


Cpdf.getMediaBox(Cpdf.Pdf, Int32, Double@, Double@, Double@, Double@)


These functions get a box given the document, page number, min x, max x, 
min y, max y in points. Only succeeds if such a box exists, as checked by
hasBox.


Cpdf.getCropBox(Cpdf.Pdf, Int32, Double@, Double@, Double@, Double@)


These functions get a box given the document, page number, min x, max x, 
min y, max y in points. Only succeeds if such a box exists, as checked by
hasBox.


Cpdf.getTrimBox(Cpdf.Pdf, Int32, Double@, Double@, Double@, Double@)


These functions get a box given the document, page number, min x, max x, 
min y, max y in points. Only succeeds if such a box exists, as checked by
hasBox.


Cpdf.getArtBox(Cpdf.Pdf, Int32, Double@, Double@, Double@, Double@)


These functions get a box given the document, page number, min x, max x, 
min y, max y in points. Only succeeds if such a box exists, as checked by
hasBox.


Cpdf.getBleedBox(Cpdf.Pdf, Int32, Double@, Double@, Double@, Double@)


These functions get a box given the document, page number, min x, max x, 
min y, max y in points. Only succeeds if such a box exists, as checked by
hasBox.


Cpdf.setMediabox(Cpdf.Pdf, List{Int32}, Double, Double, Double, Double)


These functions set a box given the document, page range, min x, max x, 
min y, max y in points.


Cpdf.setCropBox(Cpdf.Pdf, List{Int32}, Double, Double, Double, Double)


These functions set a box given the document, page range, min x, max x, 
min y, max y in points.


Cpdf.setTrimBox(Cpdf.Pdf, List{Int32}, Double, Double, Double, Double)


These functions set a box given the document, page range, min x, max x, 
min y, max y in points.


Cpdf.setArtBox(Cpdf.Pdf, List{Int32}, Double, Double, Double, Double)


These functions set a box given the document, page range, min x, max x, 
min y, max y in points.


Cpdf.setBleedBox(Cpdf.Pdf, List{Int32}, Double, Double, Double, Double)


These functions set a box given the document, page range, min x, max x, 
min y, max y in points.


Cpdf.markTrapped(Cpdf.Pdf)


Marks a document as trapped.


Cpdf.markUntrapped(Cpdf.Pdf)


Marks a document as untrapped.


Cpdf.markTrappedXMP(Cpdf.Pdf)


Marks a document as trapped in XMP metadata.


Cpdf.markUntrappedXMP(Cpdf.Pdf)


Marks a document as untrapped in XMP metadata.


Cpdf.Layout

Layouts

Cpdf.Layout.SinglePage

Single page

Cpdf.Layout.OneColumn

One column

Cpdf.Layout.TwoColumnLeft

Two column left

Cpdf.Layout.TwoColumnRight

Two column right

Cpdf.Layout.TwoPageLeft

Two page left

Cpdf.Layout.TwoPageRight

Two page right

Cpdf.setPageLayout(Cpdf.Pdf, Cpdf.Layout)


Sets the page layout for a document.


Cpdf.PageMode

Page modes

Cpdf.PageMode.UseNone

Use none

Cpdf.PageMode.UseOutlines

Use outlines

Cpdf.PageMode.UseThumbs

Use thumbs

Cpdf.PageMode.UseOC

Use OC

Cpdf.PageMode.UseAttachments

Use attachments

Cpdf.setPageMode(Cpdf.Pdf, Cpdf.PageMode)


Sets the page mode for a document.


Cpdf.hideToolbar(Cpdf.Pdf, Boolean)


Sets the hide toolbar flag.


Cpdf.hideMenubar(Cpdf.Pdf, Boolean)


Sets the hide menubar flag.


Cpdf.hideWindowUi(Cpdf.Pdf, Boolean)


Sets the hide window UI flag.


Cpdf.fitWindow(Cpdf.Pdf, Boolean)


Sets the fit window flag.


Cpdf.centerWindow(Cpdf.Pdf, Boolean)


Sets the center window flag.


Cpdf.displayDocTitle(Cpdf.Pdf, Boolean)


Sets the display doc title flag.


Cpdf.openAtPage(Cpdf.Pdf, Boolean, Int32)


Sets the PDF to open, possibly with
zoom-to-fit, at the given page number.


Cpdf.setMetadataFromFile(Cpdf.Pdf, String)


Sets the XMP metadata of a
document, given a file name.


Cpdf.setMetadataFromByteArray(Cpdf.Pdf, Byte[])


Sets the XMP metadata from
an array of bytes.


Cpdf.removeMetadata(Cpdf.Pdf)


Removes the XMP metadata from a document.


Cpdf.getMetadata(Cpdf.Pdf)


Returns the XMP metadata from a document.


Cpdf.createMetadata(Cpdf.Pdf)


Builds fresh metadata as best it can from
existing metadata in the document.


Cpdf.setMetadataDate(Cpdf.Pdf, String)


Sets the metadata date for a PDF. The date
is given in PDF date format -- cpdf will convert it to XMP format. The
date 'now' means now.


Cpdf.PageLabelStyle

Page label styles

Cpdf.PageLabelStyle.DecimalArabic

1, 2, 3...

Cpdf.PageLabelStyle.UppercaseRoman

I, II, III...

Cpdf.PageLabelStyle.LowercaseRoman

i, ii, iii...

Cpdf.PageLabelStyle.UppercaseLetters

A, B, C...

Cpdf.PageLabelStyle.LowercaseLetters

a, b, c...

Cpdf.addPageLabels(Cpdf.Pdf, Cpdf.PageLabelStyle, String, Int32, List{Int32}, Boolean)


Adds page labels. The prefix is prefix text for each label. The range is the page range the
labels apply to. Offset can be used to shift the numbering up or down.


Cpdf.removePageLabels(Cpdf.Pdf)


Removes the page labels from the document.


Cpdf.getPageLabelStringForPage(Cpdf.Pdf, Int32)


Calculates the full label
string for a given page, and returns it.


Cpdf.startGetPageLabels(Cpdf.Pdf)



Cpdf.getPageLabelStyle(Int32)



Cpdf.getPageLabelPrefix(Int32)



Cpdf.getPageLabelOffset(Int32)



Cpdf.getPageLabelRange(Int32)



Cpdf.endGetPageLabels



Cpdf.dummych12

